### 2013-07-10 tests_Housing.Rmd
added Housing and Cal-Housing datasets

```{r, message = FALSE, tidy = FALSE, echo = F}
## knitr configuration: http://yihui.name/knitr/options#chunk_options
opts_chunk$set(comment = "", error= TRUE, warning = FALSE, message = FALSE,
               tidy = FALSE, cache = TRUE, echo = T,
               fig.width = 6, fig.height = 6)
```
Testing Auto-Mpg
========================================================

@@

filename <- "Auto-Mpg/auto.data"  # where is the data (under dataset folder)
filepath <- paste0("datasets/",filename)
my.data <- read.csv(filepath, header=FALSE)

@@

sapply(my.data, class)
my.data$x3 <- as.numeric(my.data$x3) # x3 was a factor, make it a numeric value
head(my.data,8)

@@

save(report, file="Auto-Mpg300.Rda") # recover with load("Auto-Mpg300.Rda")

@@

write.table(df, "Auto-Mpg300.txt")

@@

qplot(method,error,data=df,geom=c("jitter","boxplot")) + 
  ylab("root-mean-square error") + 
  xlab("regression method") +
  ggtitle("Auto-Mpg dataset")

@@

write.table(df, "lambda.errors.Auto-Mpg.txt")

df <- read.table("lambda.errors.Auto-Mpg.txt", header=TRUE)

@@

library(ggplot2)
qplot(lambda,error,data=df,geom=c("jitter","boxplot")) + 
  ylab("root-mean-square error") + 
  xlab("lambda value") +
 # coord_cartesian(ylim = c(0, 50))  +
  ggtitle("Auto-Mpg dataset")
##############################################
# Check fitness progress

>>>>

```{r, message = FALSE, tidy = FALSE, echo = F}
## knitr configuration: http://yihui.name/knitr/options#chunk_options
opts_chunk$set(comment = "", error= TRUE, warning = FALSE, message = FALSE,
               tidy = FALSE, cache = TRUE, echo = T,
               fig.width = 6, fig.height = 6)
```
Testing Housing
========================================================

@@

filename <- "Housing/housing.data"  # where is the data (under dataset folder)
filepath <- paste0("datasets/",filename)
my.data <- read.csv(filepath, header=FALSE)

@@

sapply(my.data, class)
# my.data$x3 <- as.numeric(my.data$x3) # x3 was a factor, make it a numeric value
head(my.data,8)

@@

save(report, file="Housing300.Rda") # recover with load("Housing300.Rda")

@@

write.table(df, "Housing300.txt")

@@

qplot(method,error,data=df,geom=c("jitter","boxplot")) + 
  ylab("root-mean-square error") + 
  xlab("regression method") +
  ggtitle("Housing dataset")

@@

write.table(df, "lambda.errors.Housing.txt")

df <- read.table("lambda.errors.Housing.txt", header=TRUE)

@@

library(ggplot2)
qplot(lambda,error,data=df,geom=c("jitter","boxplot")) + 
  ylab("root-mean-square error") + 
  xlab("lambda value") +
 # coord_cartesian(ylim = c(0, 50))  +
  ggtitle("Housing dataset")
##############################################
# Check fitness progress
